ECE 612, Information Theory

### 2024-04-03 information-theory/main.tex
Checkpoint on 612 cheatsheet

@@

@@

\section{Gaussian channel}
\begin{definition}[Gaussian channel with power constraint]

\end{definition}

\begin{definition}[Information channel capacity]

\end{definition}

>>>>

\begin{theorem}[Joint normality implies marginal normality]
    If $\mathbf{X} = (X_1, X_2, \ldots, X_n)$ follows a joint normal distribution, then any linear combination of $\mathbf{X}$ follows normal distribution.
\end{theorem}

@@

\begin{theorem}[Fano's inequality]
    Let $X \rightarrow Y \rightarrow \hat{X}$ represent an encode-decode process, where $X, \hat{X} \in \mathcal{X}$ have the same support. Let $e$ denote decoding error $\hat{X} \neq X$, then:

    $$
    H(X \mid Y) \leq H(P_e) + P_e \log(\norm{\mathcal{X}})
    $$
\end{theorem}

@@

\section{Gaussian channel}
\begin{definition}[Information channel capacity]
    Let $Y = X + Z$, where $Z \leftsample N(0, \sigma^2)$ and $E[X^2] \leq P$ for some power level constraint $P$. The \textbf{information channel capacity} is defined by

    $$
    C^I = \max_{f_X : E[X^2] \leq P} I(X; Y)
    $$
\end{definition}
